\textbf{EECS 340: Assignment 5}

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 1(c) responses.

>>>>

\paragraph{(i)} Determine what edit to make (or not making any edit) when reached the last character of $X$.

\paragraph{(iii)}
Let $X_k = x_1x_2...x_k$ and likewise for $Y_k$.

\begin{itemize}
    \item Subproblem: $D(i, j)$ provides the shortest edit distance between $X_i$ and $Y_j$.
    \item Overall problem: $D(m, n)$ provides the shortest edit distance between $X_m$ and $Y_n$.
\end{itemize}

\begin{equation}
    D(i, j) =
    \begin{cases}
        j & \text{if \ } i = 0 \\
        i & \text{if \ } j = 0 \\
        D(i-1, j-1) & \text{if \ } x_i = y_j \\
        min\{D(i, j-1) + 1, D(i-1, j) + 1, D(i-1, j-1) + 1  \} & \text{otherwise}\\
    \end{cases}\nonumber
\end{equation}

\paragraph{(v)}
We have $T(n) = \Theta(mn)$. A matrix of $m \cdot n$ is filled when two strings are listing their possible reductions of chars, thus there are $\Theta(mn)$ subproblems. Each subproblem takes $\Theta(1)$ to execute.\\
$\Longrightarrow T(n) =  \Theta(mn) \cdot \Theta(1) =  \Theta(mn)$
